Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-15 chi2012.tex
working on brushing

\subsubsection{Coreference management: Drag-and-Drop Same-As}

@@

Related to the concept of co-reference, we extended the drag-and-drop sameas support to also be used to consolidate inconsistant enumerated values of properties, such as ``Casual dining'' vs ``Relaxed'' so that they can be uniformly compared. This allows the creation of meaningful, de-duplicated histograms and other visualisations.

>>>>

\subsubsection{Coreference consolidation: Drag-and-Drop Same-As}

@@

Related to the concept of co-reference, PS2 revealed that enumerated values of properties were often inconsistent, e.g. ``Casual dining'' vs ``Relaxed'' for a restaurant's ``atmosphere'' property. To reoncile such differences, so that they can be uniformly compared, we extended the drag and drop support of co-reference combination to support enumerated literal values as well,  This effectively allowed de-duplicated histograms and other visualisations to be made.
